\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref} % Hyperref package for url's and [hidelinks] option to remove collouring\
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tabularx, makecell}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{csquotes}
\usepackage{float}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{lineno}
\linenumbers
%\usepackage{showframe} %This line can be used to clearly show the new margins

\newgeometry{vmargin={15mm}, hmargin={12mm,17mm}}   % set the margins

\usetikzlibrary{positioning,fit,calc,arrows.meta}
\tikzstyle{myarrows}=[line width=1mm,-triangle 45,postaction={draw, line width=3mm, shorten >=4mm, -}]

\title{The assessment of A on B under conditions C, D, and E}
\author{Author and Supervisor}

\begin{document}

\maketitle
\tableofcontents

\begin{abstract}
A is important because things. 
A has an impact on B in certain ways.
We hypothesize that D and E influence this interaction with some outcomes based on supporting information. 
The effect was tested on a tiny number of participants, manipulating A in conditions D and E, with control condition C.
We found significant effects of D and E on B.
This result is important because reasons.
There are several caveats.
Future work will include doing stuff.
\end{abstract}
\newpage
\section{Introduction}
Some background on A and B.
The support for why D and E and interesting manipulations to try.
\section{Methods}
General information about the experiment.
\subsection{Participants}
Information about the participants
\subsection{Experimental Stimuli}
Information about the stimuli
\subsection{Measurement}
Information about the measurement procedure
\subsection{Experimental Design and Procedure}
Further details needed to replicate the experiment procedure/

\section{Results}
Details about how the data was analyzed, including which models and packages were included.
\subsection{Correlation}
How the data did or did not correlate
\subsection{Linear Mixed-Effects Models}
The statistical modeling that was performed.
Testing the assumptions of the models to inform the reader if the models are valid.
\section{Discussion}
Summarize the core finding, and why this is important.
\subsection{Limitations \& Further Research}
What improvements could be made to this work, and what further work is required.
\section{Conclusions}
Summarize the work and the outcome.
\section{Conflict of interest}
The authors declare that they have no conflict of interests.
\section{Data availability statement}
Where the data and code is available.
\section{Acknowledgments}
Who paid for the work and who helped you out.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}
